### 2018-07-07 report.tex

%% Sets page size and margins
%\usepackage[a4paper,top=2.5cm,bottom=2cm,left=2.5cm,right=2.5cm,marginparwidth=1.75cm]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{font={small},skip=0.25\baselineskip}
\captionsetup[subfigure]{font={footnotesize}, skip=1pt, singlelinecheck=false}
\graphicspath{{./plots/}{./figures/}}

@@

 The combination of both programes enabled the identification and validation (matching) of thousands of spectra with high confidence in all samples (see figure \ref{fig:match_percent}). However, when compared to the total amount of spectra available, the percentage of matched spectra was on average 37.4\%, with a marked decrease starting at fraction 14.

@@

>>>>

%% Sets page size and margins
%\usepackage[a4paper,top=2.5cm,bottom=2cm,left=2.5cm,right=2.5cm,marginparwidth=1.75cm]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{font={small},skip=0.25\baselineskip}
\captionsetup[subfigure]{font={bf, footnotesize}, skip=1pt, singlelinecheck=false}
\graphicspath{{./plots/}{./figures/}}

@@

The combination of both programs enabled the identification and validation (matching) of thousands of spectra with high confidence in all samples . However, when compared to the total amount of spectra available, the percentage of matched spectra was on average 37.4\%, with a marked decrease starting at fraction 14 (see figure \ref{fig:match_percent}).

@@

\begin{figure}[!h]
\includegraphics[width=\textwidth]{match_percent}
\caption{}
\label{fig:match_percent}
\end{figure}
